\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

% Font options
\usepackage[default]{sourcesanspro}
\usepackage[T1]{fontenc}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-7pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%----------CUSTOM COMMANDS----------
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      #1 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Devi Mutyala} \\ \vspace{2pt}
    \small \href{mailto:dm53776@eid.utexas.edu}{\underline{dm53776@eid.utexas.edu}} ~ $\vert$ ~ 
    \href{mailto:mutyala.devi17@gmail.com}{\underline{mutyala.devi17@gmail.com}} ~ $\vert$ ~
    \href{https://mutyaladevi17.github.io/}{\underline{mutyaladevi17.github.io}} ~ $\vert$ ~
    \href{https://github.com/mutyaladevi17}{\underline{github.com/mutyaladevi17}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Texas at Austin}{2021 -- 2026}
      {Ph.D. in Mechanical Engineering, Oden Institute (GPA: 3.95/4.0)}{Austin, TX}
    \resumeSubheading
      {Indian Institute of Technology, Delhi}{2019}
      {M.S. (Research) in Mechanical Engineering (CGPA: 9.22/10)}{New Delhi, India}
    \resumeSubheading
      {Indian Institute of Technology, Kanpur}{2016}
      {B.Tech. in Aerospace Engineering (CGPA: 8.2/10)}{Kanpur, India}
  \resumeSubHeadingListEnd


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{AI/ML Frameworks}{: PyTorch, Hugging Face Transformers, Scikit-Learn, TensorFlow, OpenCV, torchvision} \\
     \textbf{LLMs \& Gen AI}{: OpenAI API (GPT-4, Whisper, TTS), LangChain, Litellm, Ollama, Google Gemma, Meta Llama, Gemini, LoRA / QLoRA, Fine-tuning, Prompt Engineering, Agentic AI, RAG} \\
     \textbf{Data Science Tools}{: Gradio, BeautifulSoup, SQLite, MLOps (SageMaker), Jupyter, Git, Docker, Requests, lxml} \\
     \textbf{Programming \& DB}{: Python, SQL, ChromaDB, MongoDB, ReactJS, R, MATLAB, Fortran, C} \\
     \textbf{Engineering Software}{: LAMMPS, COMSOL, ANSYS Fluent, SpaceClaim, PTC Creo, ParaView} \\
     \textbf{Relevant Coursework}{: Fine Tuning Open Source LLMs, Deep Learning, Multimodal Systems, Machine Learning with Python, Data Science Lab, Software Engineering \& Design, LLM Engineering}
    }}
 \end{itemize}


%-----------EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Intel Corporation - Data Scientist (Internship)}{June 2025 -- Dec. 2025}
      {Design \& Patterning AI Group (DPAI)}{Santa Clara, CA}
      \resumeItemListStart
        \resumeItem{Engineered interpretable deep-learning defect detection architectures for semiconductor chip layouts; constructed an end-to-end \textbf{Computer Vision (CV)} pipeline capable of layout-to-image generation and model training.}
        \resumeItem{Developed robust ML workflows to address \textbf{severely limited labeled data} ($\sim 100$ samples) and \textbf{zero non-defect data}.}
        \resumeItem{Designed and implemented a CNN-based \textbf{Prototypical Part Network (ProtoPNet)} to manage representative defect prototypes, optimizing for high coverage across defects. This enabled \textbf{explainable AI (XAI)} feature analysis.}
        \resumeItem{Integrated a modular, \textbf{end-to-end ML pipeline} encompassing data augmentation, model training, and results visualization into an existing defect commonality detection codebase.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{AI \& Machine Learning Projects}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{\href{https://github.com/mutyaladevi17/RAG-advancedRetrevial}{Advanced Retrieval-Augmented Generation (RAG) System}} $|$ \emph{LangChain, OpenAI API, Litellm, ChromaDB, Gradio}}{}
          \resumeItemListStart
            \resumeItem{Architected a sophisticated dual-pipeline RAG system, benchmarking a baseline \textbf{LangChain} implementation against a custom-built advanced retrieval engine utilizing \textbf{OpenAI SDK} and \textbf{Litellm} for superior querying.}
            \resumeItem{Engineered an advanced ingestion pipeline featuring \textbf{semantic document segmentation} and zero-shot \textbf{LLM chunk summarization} to radically maximize embedding contextual density within local \textbf{ChromaDB} vector storage collections.}
            \resumeItem{Implemented dynamic \textbf{query rewriting}, multi-query concurrent retrieval, and precise \textbf{LLM-based reranking}, boosting performance over the \textbf{baseline LangChain MRR (0.85) to an exceptional 0.88 MRR}.}
            \resumeItem{Developed a comprehensive \textbf{LLM-as-a-judge evaluation framework} with interactive \textbf{Gradio} dashboards, validating improvements from the \textbf{92\% baseline to a 95.5\% keyword coverage rating} and increasing absolute accuracy to \textbf{4.51/5}.}
          \resumeItemListEnd

    \resumeProjectHeading
          {\textbf{\href{https://github.com/mutyaladevi17/visual-question-answer}{Medical Visual Question Answering (VQA)}} $|$ \emph{Gemma, LoRA, Hugging Face, Gemini, BioCLIP, DenseNet, BERT}}{}
          \resumeItemListStart
            \resumeItem{Built a multimodal Medical Visual Question Answering (VQA) system leveraging the comprehensive \textbf{VQA-RAD dataset} to autonomously generate highly detailed clinical explanations and diagnostic insights for complex radiology scans.}
            \resumeItem{Fine-tuned a generative text model (\textbf{Gemma-3-4B-it}) via \textbf{QLoRA}, and engineered a custom descriptive dataset using \textbf{Gemini-2.0} to augment short-answer inputs for enhanced training convergence (\textbf{BLEU 0.23, ROUGE F1: 0.48}).}
            \resumeItem{Developed high-accuracy benchmark classification pipelines utilizing foundational visual models including \textbf{BioCLIP + BERT} alongside custom architectures integrating \textbf{DenseNet121 + BiLSTM} for robust baseline validation.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{\href{https://github.com/mutyaladevi17/multimodal-flight-assistant}{Multimodal Flight Assistant}} $|$ \emph{Agentic AI, OpenAI Tool Calling, Whisper, PyTorch, SQL}}{}
          \resumeItemListStart
            \resumeItem{Architected a highly scalable \textbf{multi-agent system} featuring a \textbf{dual-LLM orchestration architecture} to dynamically route open-ended dialogue intent and normalize geographic entities for executing complex flight booking workflows.}
            \resumeItem{Engineered an \textbf{Agentic AI} pipeline securely leveraging \textbf{OpenAI Tool Calling} to map conversational user intent precisely to real-time \textbf{SQL} database queries, enabling autonomous ticket price retrieval and immediate dynamic UI updates.}
            \resumeItem{Built a complete end-to-end multi-modal conversational interface seamlessly integrating \textbf{OpenAI Whisper (STT)}, generalized \textbf{TTS} engines, and \textbf{Gradio} frontends to deploy entirely hands-free voice-to-voice interactive application flows.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{\href{https://github.com/mutyaladevi17/smart-audio-scribe}{Smart Audio Scribe}} $|$ \emph{OpenAI Whisper, Pyannote, Meta Llama, Hugging Face, PyTorch}}{}
          \resumeItemListStart
            \resumeItem{Architected an end-to-end \textbf{Speech-to-Text (STT)} integration pipeline comprehensively leveraging \textbf{OpenAI Whisper} for high-fidelity transcription alongside \textbf{Pyannote} for precise \textbf{speaker diarization} of complex multi-speaker audio recordings.}
            \resumeItem{Engineered a complete \textbf{Generative AI} engine operating purely on local \textbf{Meta Llama LLMs} via \textbf{Hugging Face Transformers} to securely and autonomously parse raw transcripts and synthesize structured \textbf{context-aware meeting minutes}.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{\href{https://github.com/mutyaladevi17/AI-financial-news-engine}{AI Financial News Engine}} $|$ \emph{GPT-4o, GPT-5-nano, BeautifulSoup, Python, Requests}}{}
          \resumeItemListStart
            \resumeItem{Engineered a rapid intelligent financial data pipeline utilizing \textbf{GPT-5-nano} to continuously and autonomously classify, filter, and extract the most objectively relevant market news from heavily web-scraped (\textbf{BeautifulSoup}) Yahoo Finance web page.}
      %       \resumeItem{Integrated advanced \textbf{GPT-4o} LLM agents to automatically synthesize unstructured extracted content directly into professional, highly structured \textbf{stock news summaries}, managing high-volume enterprise data extraction alongside robust error handling.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{\href{https://github.com/mutyaladevi17/find_common_object}{Find Common Object (Explainable AI / ProtoPNet)}} $|$ \emph{PyTorch, torchvision, CNN, Matplotlib}}{}
          \resumeItemListStart
            \resumeItem{Developed a convolutional neural network (\textbf{CNN}) \textbf{Explainable AI} model implementing Prototypical Part Networks (\textbf{ProtoPNet}) to discover, isolate, and precisely localize common sub-objects across visual datasets.}
            \resumeItem{Designed sophisticated deep learning models that inherently learn human-interpretable image structural prototypes rather than black-box embeddings, visually providing spatial localization strictly through \textbf{bounding boxes} and rich \textbf{heatmaps}.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd

   % \resumeProjectHeading
   %    {\textbf{\href{https://github.com/mutyaladevi17/AI-financial-news-engine}{AI Financial News Engine}} $|$ \emph{GPT-4o, GPT-5-nano, BeautifulSoup, Python, Requests}}{}
   %    \resumeItemListStart
   %      \resumeItem{Engineered a rapid intelligent financial data pipeline utilizing \textbf{GPT-5-nano} to continuously and autonomously classify, filter, and extract the most objectively relevant market news from heavily web-scraped (\textbf{BeautifulSoup}) Yahoo Finance web pages.}
   %      \resumeItem{Integrated advanced \textbf{GPT-4o} LLM agents to automatically synthesize unstructured extracted content directly into professional, highly structured \textbf{stock news summaries}, managing high-volume enterprise data extraction alongside robust error handling.}
   %    \resumeItemListEnd

%-----------RESEARCH & ENGINEERING EXPERIENCE-----------
\section{Engineering \& Research Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Oden Institute, University of Texas at Austin -- Graduate Researcher}{Sept. 2022 -- May 2025}
      {Advisor: Prof. Narayana Aluru}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Investigating complex physics of nanoscale systems to explore the development of a \textbf{nanofluidic memristor}.}
        \resumeItem{Employing \textbf{Molecular Dynamics simulations (LAMMPS)} and \textbf{Poisson-Nernst-Planck continuum models (COMSOL)} to analyze ionic transport and electrokinetic behavior in nanoscale environments.}
        \resumeItem{Utilizing \textbf{Python} to develop analytical frameworks and conduct comprehensive \textbf{data analysis}, uncovering insights connecting physical mechanisms with anomalies in large-scale simulation results.}
      \resumeItemListEnd

    \resumeSubheading
      {Indian Institute of Technology, Madras -- Project Associate}{Aug. 2020 -- Apr. 2021}
      {Department of Aerospace Engineering}{Chennai, India}
      \resumeItemListStart
        \resumeItem{Executed \textbf{Large-Eddy Simulations (LES)} of high Reynolds number channel flows with non-equilibrium effects.}
        \resumeItem{Implemented \textbf{wall-modeled LES (wall stress model)} for non-equilibrium flows and sensor-based computations for accurate transition flow modeling into high-fidelity \textbf{in-house CFD solvers}.}

      \resumeItemListEnd

    \resumeSubheading
      {Havells India Ltd. -- Research Engineer}{July 2019 -- Aug. 2020}
      {Center for Research and Innovation}{Delhi, India}
      \resumeItemListStart
        \resumeItem{\textbf{Patented Venturi Air Cooler:} Designed an energy-efficient device eliminating water pumps by harnessing pressure/temperature profiles. Secondary inventor on patent \textbf{IN202011018315}.}
        \resumeItem{Developed analytical models leveraging \textbf{Blade Element theory} and \textbf{CFD} to design aerodynamic hardware, significantly improving volumetric flow rates and \textbf{minimizing power consumption} before scalable production.}
      \resumeItemListEnd
      
    \resumeSubheading
      {University of Texas at Austin / IIT Delhi -- Teaching Assistant}{2017 -- 2025}
      {Mechanical Engineering Departments}{Austin, TX \& Delhi, India}
      \resumeItemListStart
        \resumeItem{Instructed tutorial sessions and conducted automated evaluations using Python for Applied Thermodynamics (2025), Computational Fluid Dynamics (2022), Propulsion (2021), and Gas Dynamics (2018).}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PUBLICATIONS & PATENTS-----------
\section{Publications \& Patents}
  \resumeSubHeadingListStart
    \resumeSubItem{\textbf{Publications:} \textit{Ozonated Monolayer Graphene for Extended Performance and Durability in Hydrogen Fuel Cell Electric Vehicles.} Devi Mutyala, Deji Akinwande, et al. ACS Nano (2025).}
    \resumeSubItem{\textbf{Publications:} \textit{Room-Temperature Pulsed Laser Deposition of Boron Nitride for Enhanced Fuel Cell Selectivity.} Devi Mutyala, Deji Akinwande, et al. ACS Nano (2025).}
    \resumeSubItem{\textbf{Patents:} \textit{Venturi Air Cooler.} Issued January 17, 2024. Patent Number IN202011018315.}
  \resumeSubHeadingListEnd

%-----------AWARDS & ACHIEVEMENTS-----------
\section{Awards \& Achievements}
  \resumeSubHeadingListStart
    \resumeSubItem{\textbf{Academic Awards:} Recipient of the \textbf{UT Austin Engineering Fellowship} (2021-2025) and the \textbf{IIT Kanpur Academic Excellence Award} awarded to the top 5\% of the class (2014-2015).}
    \resumeSubItem{\textbf{Leadership and Service:} Recipient of the \textbf{Institute Blues} (2016), the highest honor at IIT Kanpur for exceptional sports leadership and institutional impact as Team Captain and Deputy Contingent Leader.}
    \resumeSubItem{\textbf{Athletics Achievements:} Attained 8 Inter IIT Athletics records and 11 Gold medals in track and field at IIT. Served as Captain of the Institute Athletics Team and Deputy Contingent Leader.}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
